---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
set.seed(0)
```

# GradAdaptCompExp

<!-- badges: start -->
<!-- badges: end -->

The goal of GradAdaptCompExp is to provide code for managing computer experiments.

This code was from my (Collin Erickson) PhD work for the paper
[Gradient-based criteria for sequential experiment design](https://onlinelibrary.wiley.com/doi/10.1002/qre.2981).

## Installation

You can install the development version of GradAdaptCompExp from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("CollinErickson/GradAdaptCompExp")
```

## Example

Here's an example of how to use the code.

First, load the R package.

```{r load library}
library(GradAdaptCompExp)
## basic example code
```

```{r set seed, include=F}
set.seed(1)
```

Second, use `adapt.concept2.sFFLHD.R6$new` to create a new experiment.
`adapt.concept2.sFFLHD.R6` is an R6 class with many associated methods,
so we are just initializing a new instance of this class.

```{r create exp}
# wing weight, grad_norm2_mean, laGP_GauPro_kernel
a <- adapt.concept2.sFFLHD.R6$new(
  D=10,L=5,func=TestFunctions::wingweight, 
  nugget=1e-7, estimate.nugget = TRUE,
  obj="desirability", des_func=des_func_grad_norm2_mean,
  actual_des_func=NULL,
  stage1batches=6,
  design='sFFLHD_Lflex',
  error_power=2,
  selection_method="max_des_red_all_best"
); 
```

Here's what all the parameters we just gave in mean:

1. `D=10`: There are 10 input dimensions for the function.

1. `L=5`: We will evaluate in batches of size 5.

1. `func=TestFunctions::wingweight`: This is the function we are evaluating.
In this case it is the Wing Weight function, which has 10 input dimensions
(we already told it `D=10`), from the `TestFunctions` package.

1. `nugget = 1e-7`: When fitting the Gaussian process model to the data,
we will start with a nugget of 1e-7. 

1. `estimate.nugget = TRUE`: The nugget for the GP model will be estimated.
This is recommended unless you know there is no noise in the function,
and even then should probably be `TRUE`.

1. `obj="desirability"`: This tells it how to pick points. `desirability` means
it will pick points according to a criterion.

2. `des_func=des_func_grad_norm2_mean`: This tells it which desirability
function to use. In this case it is `des_func_grad_norm2_mean`, which
is the gradient of the norm squared of the mean.

2. `actual_des_func=NULL`: This is where we would give it true desirability
function so that it can compare its predictions to the true values.
In general this won't be known and can be left as NULL or ignored completely.

2. `stage1batches=6`: This is the number of stage 1 batches to use. In stage 1
the points are just chosen using the space filling design, not according to
the desirability criterion. In this case, the total number of points chosen
this way will be `6*5=30`, the 5 coming from `L` above.

2. `design='sFFLHD_Lflex'`: This tells it how to generate candidate points.
This will use points from an sFFLHD, but will be flexible on the batch size.
If you don't let it be flexible, it may not be able to find a suitable sFFLHD
for the given batch size.

3. `error_power=2`: Either 1 or 2. Whether you want to reduce the absolute error (1)
or squared error (2).

2. `selection_method="max_des_red_all_best"`: This tells it that the points
should be chosen to give the maximum reduction is desirability.

Here we actually start running the experiment using the `run` method.
We tell it to run 6 batches, which matches the number of space
filling batches.

```{r e1 run 1}
a$run(6, noplot = TRUE)
```

Now we tell it to plot its progress.

The top left plot shows how the predicted integrated weighted error (PIWE) is decreasing.
Since we didn't give it the actual desirability (weight) function, it can't plot the IWE.

The top right plot is showing how accurate the model predictions are.
The x-axis is the true values, and the y-axis is the prediction residual.
The red points (Z) are for the data we have collected. They have perfect predictions
since they are included in the model.
The black points (ZZ) are when predicting at new points. The green bars are the 95%
prediction intervals. Note that we haven't evaluated these points yet in the experiment,
but it is evaluating these points for the plot. In reality we wouldn't do this
since we wouldn't have those points.

The bottom left plot shows the percentage of candidate points that we have
evaluted. Since we have been in stage 1 (space filling), it's just using
all the points in order, so no points have been ignored.

The bottom right plot shows the desirability on the x-axis for a sample
of points. The black marks the predicted standard error from the GP model.
The red marks the actual absolute error for these points, which is only
done since we know the function be evaluated quickly.

```{r e1 plot 1}
a$plot1()
```

If we continue running the experiment, it will start to choose points
using the desirability function.

```{r e1 run 2}
a$run(6, noplot = TRUE)
```
Here are the updated plots.
The top left plot is showing that the PIWE is decreasing at a steady
rate as more data is collected.
The bottom left plot is showing that we are using a smaller percentage
of all available points. This is good, it means it is being adaptive
and not just using the points from the space filling design.

```{r e1 plot 2}
a$plot1()
```
